Improving inference of evolutionary history

### 2014-11-02 slides/osu/slides.tex
More work on osu slides.

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Southeast Asia}    
\end{frame}
}

@@

@@

\begin{frame}
\begin{columns}[c]
    \column{.5\textwidth}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/cyrt-agusanensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=1.5cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1>[height=1.5cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
    \column{.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \includegraphics<2>[width=\textwidth]{../images/maps/Philippines-negros_panay.png}
\end{columns}
\end{frame}

\section{Empirical results}
\subsection{Too good to be true?}

% \begin{frame}
% \frametitle{Outline}
% \tableofcontents[currentsection,currentsubsection]
% \end{frame}

\begin{frame}
    \frametitle{Empirical results}
    \begin{columns}[c]
        \column{.4\textwidth}
            {\small
            Strong support for simultaneous divergence of all 22 taxon pairs \\
            \vspace{1cm}
            pp $>$ 0.96 \\
            \vspace{1cm}
            $\sim$100,000--250,000 years ago}
        \column{.6\textwidth}
        \includegraphics[width=\textwidth]{../images/jointDensityPlotsSlide.jpg}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{Simulation-based power analyses}
    What is ``simultaneous''?
    \begin{myitemize}
        \item<1-> Simulate datasets in which all 22 divergence times are random
        \uncover<1->{
            \smallskip
            \begin{myitemize}
                \item $\divTime{} \sim U(0, \,0.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,1.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,2.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,5.0 \,MGA)$
                \smallskip
            \end{myitemize}
        \item<1-> $MGA$ = Millions of Generations Ago
        }
        \item<2-> Simulate 1000 datasets for each \divTime{} distribution
        \item<2-> Analyze all 4000 datasets as we did the empirical data
    \end{myitemize}
\end{frame}

\begin{frame}[t]
    \frametitle{Simulation-based power analyses: Results}
    \vspace{1cm}
        \centerline{
        \includegraphics[width=1.13\textwidth]{../images/old_old_power_psi_mode.pdf}}
        % \vspace{0mm}
        % \centerline{
        % \includegraphics<2>[width=1.13\textwidth]{../images/old-sims_power_psi_prob_headless.pdf}}
    \barefootnote{\shortfullcite{Oaks2012}}
\end{frame}

\begin{frame}
    \frametitle{Simulation-based power analyses: Results}
        \msb will often infer clustered divergences when divergences are random
        over millions of generations. \\

    \bigskip
    The empirical results are likely spurious \\

    \begin{onlyenv}<2->
        \begin{block}{Objective:}
            Use principles of probability to extend \msb framework for improved
            estimation of shared evolutionary history
        \end{block}
    \end{onlyenv}
    \barefootnote{\tiny\shortfullcite{Oaks2012}. \hspace{2mm}\shortfullcite{Oaks2014reply}}
\end{frame}

@@

\begin{frame}
    \frametitle{Prior on divergence models}
    \begin{itemize}
        \item \msb uses a discrete uniform prior on the \emph{number} of
            divergence events
    \end{itemize}
    % \smallskip
    \centerline{
        \includegraphics<1->[width=\textwidth]{../images/partition_numbers.pdf}}
    \begin{block}<2->{\it Potential solution:}
        Place flexible prior directly on the sample space of divergence models
    \end{block}
\end{frame}

\begin{frame}
    \frametitle{New method: \dppmsbayes}
    \begin{itemize}
        % \item<1-> Reparameterized the model implemented in \msb
        \item<1-> Replaced uniform priors on continuous parameters with gamma and
            beta distributions
        \item<1-> Dirichlet process prior (DPP) over all possible divergence
            models
        \item<1-> Develop multi-processing interface to improve performance for
            accommodating genomic datasets
        % \item<4-> Uniform prior over divergence models
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Simulation-based assessment}
        Simulate 50,000 datasets under three models\\
        \smallskip
        \begin{description}
            \item[$M_{msBayes}$]
                \begin{itemize}
                    \item U-shaped prior on divergence models
                    \item Uniform priors on continuous parameters
                \end{itemize}
            \smallskip
            \item[$M_{Ushaped}$]
                \begin{itemize}
                    \item U-shaped prior on divergence models
                    \item Gamma priors on continuous parameters
                \end{itemize}
            \smallskip
            % \item[$M_{Uniform}$]
            %     \begin{itemize}
            %         \item Uniform prior on divergence models
            %         \item Gamma priors on continuous parameters
            %     \end{itemize}
            % \smallskip
            \item[$M_{DPP}$]
                \begin{itemize}
                    \item DPP prior on divergence models
                    \item Gamma priors on continuous parameters
                \end{itemize}
        \end{description}
        \smallskip
        Analyze all datasets under each of the models
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Simulation results}
    \centerline{
        \includegraphics<1>[width=0.85\textwidth]{../images/validation-model-choice-old-dpp.pdf}
        \includegraphics<2>[width=1.13\textwidth]{../images/validation-model-choice-old-dpp-full.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Simulation-based power analyses}
    \begin{myitemize}
        \item Simulate datasets in which all 22 divergence times are random
        \uncover{
            \smallskip
            \begin{myitemize}
                \item $\divTime{} \sim U(0, \,0.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,1.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,2.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,5.0 \,MGA)$
                \smallskip
            \end{myitemize}
        \item $MGA$ = Millions of Generations Ago
        }
        \item Simulate 1000 datasets for each \divTime{} distribution
        % \item Analyze all 4000 datasets as we did the empirical data
        \item Analyze all 4000 datasets under models $M_{msBayes}$, $M_{Ushaped}$, and $M_{DPP}$
    \end{myitemize}
\end{frame}

\begin{frame}[t]
    \frametitle{\dppmsbayes: Power results}
    \vspace{1cm}
        \centerline{
        \includegraphics[width=1.13\textwidth]<1->{../images/old_old_power_psi_mode.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=1.13\textwidth]<2->{../images/old_dpp_power_psi_mode_headless.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}[t]
    \frametitle{\dppmsbayes: Power results}
    \vspace{1cm}
        \centerline{
        \includegraphics[width=1.13\textwidth]{../images/old_old_power_psi_prob.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=1.13\textwidth]{../images/old_dpp_power_psi_prob_headless.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Power results}
    % \vspace{1cm}
        \centerline{
        \includegraphics[width=\textwidth]{../images/old_old_power_psi_prob.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=\textwidth]{../images/old_u-shaped_power_psi_prob_headless.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=\textwidth]{../images/old_dpp_power_psi_prob_headless.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{Empirical results: Philippine diversification}
    \centerline{
    \includegraphics[width=\textwidth]{../../empirical-analyses/plots/philippines-dpp-psi-posterior-old-vs-dpp.pdf}}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item<1-> New method for estimating shared evolutionary history shows
            improved:
        \begin{enumerate}
            \item Estimation of posterior uncertainty
            \item Model-choice accuracy
            \item Power to detect temporal variation across divergences
            \item Robustness to model violations
            \item Speed!
        \end{enumerate}

    \end{itemize}

    \ignore{
    \bigskip
    \begin{uncoverenv}<2->
    Caveats:\\
    \begin{itemize}
            \item<1-> Estimating a very rich (600+ parameters for 22 taxa) model
                using limited information from the data

            \begin{itemize}
                \item Likely sensitive to prior assumptions
                \item Be skeptical of strongly supported results
            \end{itemize}

    \end{itemize}
    \end{uncoverenv}
    }
\end{frame}

\begin{frame}
    \frametitle{Recommendations}
    For Bayesian model choice, choose priors carefully\\
    \bigskip
    ABC model choice estimates should be accompanied by:
    \begin{enumerate}
        \item Simulation-based power analyses
        \item Assessment of prior sensitivity
    \end{enumerate}
\end{frame}

@@

\begin{frame}
    \frametitle{Testing limate-driven diversification}
    \textbf{Did repeated fragmentation of islands during inter-glacial rises in sea level
    promote diversification?}\\

    \bigskip
    \begin{uncoverenv}<2->
    \ldots left with uncertainty regarding climate-driven diversification \\
    \end{uncoverenv}

    \begin{uncoverenv}<3->
    \begin{itemize}
            \item More data

            \item More power 
    \end{itemize}
    \end{uncoverenv}
\end{frame}

@@

\begin{frame}
    \frametitle{Genomic data}
    \begin{columns}[c]
        \column{.5\textwidth}
        \begin{myitemize}
            \item Collecting genomic data from two gekkonid radiations
                co-distributed Southeast Asia
            \begin{myitemize}
                \item \emph{Cyrtodactylus}---12+ species
                \item \emph{Gekko}---13+ species
            \end{myitemize}
            \item Whole genome assemblies for each genus
            \item RAD-seq libraries constructed for $\approx150$ individuals
                from each genus
        \end{myitemize}
        \column{.5\textwidth}
        \includegraphics[width=\textwidth]{../images/photos/cyrt-agusanensis.jpg} \quad
        \includegraphics[width=\textwidth]{../images/photos/gekko-mindorensis.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    Prelim results from 5 population pairs/1000 loci \ldots
\end{frame}

@@

\begin{frame}
    \frametitle{Full-likelihood approach}
    \begin{itemize}[<+->]
        \item Full-likelihood Bayesian implementation \footnote{\tiny\shortfullcite{JeetDiss}}
            \begin{itemize}
                \item \ldots inefficient
            \end{itemize}
        \item Currently working on incorporating new developments on analytical
            integration of gene trees
            \footnote{\tiny\shortfullcite{Bryant2012}}
            \begin{itemize}
                \item Very efficient numerical approximation of posterior 
                \item Applicable to NGS datasets
                \item Uses all the information in the sequence data
            \end{itemize}
    \end{itemize}
\end{frame}

@@

    \begin{center}
        % \includegraphics<1->[height=5.5cm]{../images/div-model-cartoon-sp-tree-shared-wide.pdf}
        \includegraphics<1->[height=5.5cm]{../images/div-model-cartoon-sp-phylogeny.pdf}
    \end{center}
\end{frame}

@@

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../../../../Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}}
\begin{frame}
    % \frametitle{Gobi Desert}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../../../../Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}}
\begin{frame}
    % \frametitle{Gobi Desert}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../../../../Dropbox/field-photos/africa/nigeria-landscape.jpg}}
\begin{frame}
    % \frametitle{Gobi Desert}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../../../../Dropbox/field-photos/malaysia/malaysia-burungs.jpg}}
\begin{frame}
    % \frametitle{Gobi Desert}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Southeast Asia}    
\end{frame}
}

>>>>

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Southeast Asia}    
    \begin{columns}
        \column{0.6\textwidth}
        \ \\

        \column{0.45\textwidth}

        \vspace{-2.4cm}

        \begin{uncoverenv}<2->
        \colorbox{white}{
            \begin{minipage}[t][3.6cm][t]{1.1\textwidth}
                \begin{onlyenv}<2-3>
                \begin{itemize}
                    \item<2-> Repeated coalescence and fragmentation of island complexes
                    \item<3-> Prominent paradigm for explaining Philippine biodiversity
                \end{itemize}
                \end{onlyenv}

                \begin{onlyenv}<4>
                \begin{itemize}
                    \item<4> \textbf{Did repeated fragmentation of islands
                        during inter-glacial rises in sea level promote
                        diversification?}
                \end{itemize}
                \end{onlyenv}

                \begin{onlyenv}<5->
                \begin{itemize}
                    \item<5-> Climate-driven model of diversification
                    \item<6-> Testable prediction:
                    \begin{itemize}
                        \item Temporally clustered divergences among taxa
                            co-distributed across fragmented islands
                    \end{itemize}
                \end{itemize}
                \end{onlyenv}
            \end{minipage}
        }
    \end{uncoverenv}
    \end{columns}
\end{frame}
}

% \begin{frame}
%     \frametitle{Philippine Archipelago}
%     \begin{center}
%         \includegraphics<1>[width=.5\textwidth]{../images/maps/Philippines-present.png}
%         \includegraphics<2>[width=.5\textwidth]{../images/maps/Philippines.png}
%     \end{center}
% \end{frame}

% \begin{frame}
%     \frametitle{Climate-driven diversification model}
%     \begin{columns}[c]
%         \column{.5\textwidth}
%             \begin{myitemize}
%                 \item<1-> Repeated coalescence and fragmentation of island complexes
%                 \item<2-> Prominent paradigm for explaining Philippine biodiversity
%                 \item<3-> Proposed as model of diversification
%             \end{myitemize}
%         \column{.5\textwidth}
%             \includegraphics[width=\textwidth]{../images/maps/Philippines.png}
%     \end{columns}
% \end{frame}

% \begin{frame}
%     \frametitle{Testing climate-driven diversification}
%     \begin{columns}[c]
%         \column{.5\textwidth}
%     \textbf{Did repeated fragmentation of islands during inter-glacial rises in sea level
%     promote diversification?}\\
%     \bigskip
%     \uncover<2->{
%     Model has testable prediction:\\
%     \begin{itemize}
%         \item Temporally clustered divergences among taxa
%             co-distributed across fragmented islands
%     \end{itemize}
%     }
%         \column{.5\textwidth}
%             \includegraphics[width=\textwidth]{../images/maps/Philippines.png}
%     \end{columns}
% \end{frame}

@@

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Climate-driven diversification}    
    \begin{columns}
        \column{0.6\textwidth}
        \ \\

        \column{0.4\textwidth}

        \vspace{-2cm}

        \colorbox{white}{
            \begin{minipage}[t]{1.0\textwidth}
                \raggedright
                \textbf{Did repeated fragmentation of islands during
                    inter-glacial rises in sea level promote diversification?}
            \end{minipage}
        }
    \end{columns}
\end{frame}
}

@@

\begin{frame}
    \frametitle{Climate-driven diversification}
\begin{columns}[c]
    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/crocidura-beatus-DSBalete.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/sphenomorphus-abdictus-rmb.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/cyrt-agusanensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/cyrt-annulatus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/limnonectes-magnus-cds.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
        \end{minipage}

    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \includegraphics<2>[width=\textwidth]{../images/maps/Philippines-negros_panay.png}
        \begin{onlyenv}<3->
            \begin{itemize}
                \item Strong support for simultaneous divergence of all 22 taxon pairs

                \item Posterior probability $>$ 0.96 \\

                \item $\sim$100,000--250,000 years ago
            \end{itemize}
        \end{onlyenv}
        \end{minipage}
\end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{Simulation-based power analyses}
    % What is ``simultaneous''?
    \begin{myitemize}
        \item<1-> What if divergences were random?
        \item<2-> Simulate datasets in which all 22 divergence times are random
        \uncover<3->{
            \smallskip
            \begin{myitemize}
                \item $\divTime{} \sim U(0, \,0.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,1.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,2.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,5.0 \,MGA)$
                \smallskip
            \end{myitemize}
        \item<3-> $MGA$ = Millions of Generations Ago
        }
        \item<4-> Simulate 1000 datasets for each \divTime{} distribution
        \item<4-> Analyze all 4000 datasets as we did the empirical data
    \end{myitemize}
\end{frame}

\begin{frame}
    \frametitle{Simulation-based power analyses: Results}
        \centerline{
        \includegraphics[width=1.13\textwidth]{../images/old_old_power_psi_mode.pdf}}

    \begin{uncoverenv}<2->
        \begin{itemize}[<+->]
            \item \msb will often infer clustered divergences when divergences
                are random over millions of generations.

            \item The empirical results are likely spurious
        \end{itemize}
    \end{uncoverenv}

    \begin{uncoverenv}<3->
        \begin{block}{Objective:}
            Use principles of probability to extend \msb framework for improved
            estimation of shared evolutionary history
        \end{block}
    \end{uncoverenv}
    \barefootnote{\tiny\shortfullcite{Oaks2012}. \hspace{2mm}\shortfullcite{Oaks2014reply}}
\end{frame}

@@

\begin{frame}[t]
    \frametitle{Prior on divergence models}
    \begin{itemize}
        \item \msb uses a discrete uniform prior on the \emph{number} of
            divergence events
    \end{itemize}

    \begin{uncoverenv}<2->
    \begin{columns}
        \column{0.5\textwidth}
            \centerline{
                \includegraphics<2->[width=1.0\textwidth]{../images/number-of-div-models-22-unordered.pdf}}
        \column{0.5\textwidth}
            \centerline{
                \includegraphics<3->[width=1.0\textwidth]{../images/prob-of-div-models-22-unordered.pdf}}
    \end{columns}
    \end{uncoverenv}

    \begin{uncoverenv}<4->
    \begin{block}{\it Potential solution:}
        Place flexible prior directly on the sample space of divergence models
    \end{block}
    \end{uncoverenv}
\end{frame}

\begin{frame}
    \frametitle{New method: \dppmsbayes}
    \begin{itemize}[<+->]
        % \item<1-> Reparameterized the model implemented in \msb
        \item<1-> Replaced uniform priors on continuous parameters with gamma and
            beta distributions
        \item<1-> Dirichlet process prior (DPP) over all possible divergence
            models
        \item<1-> Develop multi-processing interface to improve performance for
            accommodating genomic datasets
        % \item<4-> Uniform prior over divergence models
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Simulation-based assessment}
        \uncover<1->{
        Validation:\\

        \smallskip
        \begin{itemize}
            \item Simulate 50,000 datasets and analyze each under the same
                model
        \end{itemize}
        }

        \uncover<2->{
        \bigskip
        Robustness:\\
        \begin{itemize}
            \item Simulate datasets that violate model assumptions and analyze
                each of them
        \end{itemize}
        }

        \uncover<3->{
        \bigskip
        Done for \msb and \dppmsbayes
        }
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Validation results}
    \begin{columns}
        \column{0.5\textwidth}
            \includegraphics<1->[width=1.0\textwidth]{../images/validation-model-choice-old.pdf}
        \column{0.5\textwidth}
            \includegraphics<2->[width=1.0\textwidth]{../images/validation-model-choice-dpp.pdf}
    \end{columns}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Robustness results}
    \begin{columns}
        \column{0.5\textwidth}
            \centering{
            \includegraphics<1->[width=0.9\textwidth]{../images/validation-model-choice-old-violations.pdf}
            }
        \column{0.5\textwidth}
            \centering{
            \includegraphics<1->[width=0.9\textwidth]{../images/validation-model-choice-dpp-violations.pdf}
            }
    \end{columns}

    \begin{uncoverenv}<2->
    \begin{itemize}
        \item Improved model-choice accuracy and robustness
    \end{itemize}
    \end{uncoverenv}
    \vspace{-0.5cm}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{\dppmsbayes: Simulation-based power analyses}
    Does the new method have power to detect variation in divergence times?\\

    \bigskip
    \begin{myitemize}
        \item<2-> Simulate datasets in which all 22 divergence times are random
            \smallskip
            \begin{myitemize}
                \item $\divTime{} \sim U(0, \,0.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,1.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,2.5 \,MGA)$
                \smallskip
                \item $\divTime{} \sim U(0, \,5.0 \,MGA)$
                \smallskip
            \end{myitemize}
        \item<2-> $MGA$ = Millions of Generations Ago

        \item<3-> Simulate 1000 datasets for each \divTime{} distribution
        \item<3-> Analyze all 4000 datasets with \msb and \dppmsbayes
    \end{myitemize}
\end{frame}

\begin{frame}[t]
    \frametitle{\dppmsbayes: Power results}
        \begin{onlyenv}<1-2>
        \centerline{
        \includegraphics[width=1.13\textwidth]<1-2>{../images/power-psi-old-annotate-no-pp.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=1.13\textwidth]<2>{../images/power-psi-dpp-annotate-no-pp.pdf}}
        \end{onlyenv}

        \begin{onlyenv}<3->
        \centerline{
        \includegraphics[width=1.13\textwidth]<3->{../images/power-psi-old-annotate-pp.pdf}}
        \vspace{0mm}
        \centerline{
        \includegraphics[width=1.13\textwidth]<3->{../images/power-psi-dpp-annotate-pp.pdf}}
        \end{onlyenv}

    \begin{uncoverenv}<4->
    \begin{itemize}
        \item Improved power to detect temporal variation across divergences
    \end{itemize}
    \end{uncoverenv}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Climate-driven diversification}    
    \begin{columns}
        \column{0.6\textwidth}
        \ \\

        \column{0.4\textwidth}

        \vspace{-2cm}

        \colorbox{white}{
            \begin{minipage}[t]{1.0\textwidth}
                \raggedright
                \textbf{Did repeated fragmentation of islands during
                    inter-glacial rises in sea level promote diversification?}
            \end{minipage}
        }
    \end{columns}
\end{frame}
}

\begin{frame}
    \frametitle{Climate-driven diversification}
\begin{columns}[c]
    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/crocidura-negrina-JAEsselstyn.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/crocidura-beatus-DSBalete.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/hipposideros-obscurus-MRMDuya.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/haplonycteris-fischeri-JHolden.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/sphenomorphus-abdictus-rmb.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/sphenomorphus-arborens-rmb.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/gekko-mindorensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/dendrelaphis-pictus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/cyrt-agusanensis.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/cyrt-annulatus-cds.jpg}}
        % \vspace{0.5mm}
        \centerline{
        \includegraphics<1->[height=1.3cm]{../images/photos/limnonectes-magnus-cds.jpg}
        \hspace{0.3mm}
        \includegraphics<1->[height=1.3cm]{../images/photos/limnonectes-leytensis-rmb.jpg}}
        \end{minipage}

    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \includegraphics<1>[width=\textwidth]{../images/maps/Philippines.png}
        \end{minipage}
\end{columns}
\end{frame}

\begin{frame}
    \frametitle{Empirical results}
    \centerline{
    \includegraphics[width=\textwidth]{../../empirical-analyses/plots/philippines-dpp-psi-posterior-old-vs-dpp.pdf}}

    \begin{uncoverenv}<2->
    \begin{itemize}
        \item More ``honest'' estimate of posterior uncertainty
    \end{itemize}
    \end{uncoverenv}
    \barefootnote{\shortfullcite{Oaks2014dpp}}
\end{frame}

\begin{frame}
    \frametitle{Empirical results}
    \centerline{
    \includegraphics[width=\textwidth]{../../empirical-analyses/plots/philippines-dpp-psi-posterior-prior.pdf}}
    \smallskip
    \centerline{
    \includegraphics[height=2cm]{../images/sea-level-only.pdf}}
\end{frame}

\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item<1-> New method for estimating shared evolutionary history shows
            improved:
            \begin{enumerate}
                \item<2-> Estimation of posterior uncertainty
                \item<2-> Model-choice accuracy
                \item<2-> Power to detect temporal variation across divergences
                \item<2-> Robustness to model violations
                \item<2-> Speed!
            \end{enumerate}

        \smallskip
        \item<3-> Climate-driven diversification model?
            \begin{itemize}
                \item<4-> Results consistent with prediction of clustered
                    divergences
                \item<4-> Results suggest multiple co-divergences
                \item<4-> However, there is a lot of uncertainty!
            \end{itemize}

        \smallskip
        \item<5-> What to do?
            \begin{itemize}
                \item<6-> More data!
                \item<6-> More power! 
            \end{itemize}
    \end{itemize}
\end{frame}

@@

@@

\begin{frame}
    \frametitle{More data}
    \begin{columns}[c]
        \column{.5\textwidth}
        \begin{myitemize}
            \item Collecting genomic data from two gekkonid radiations
                co-distributed Southeast Asia
            \begin{myitemize}
                \item \emph{Cyrtodactylus}---12+ species
                \item \emph{Gekko}---13+ species
            \end{myitemize}
            \item Whole genome assemblies for each genus
            \item RAD-seq libraries constructed for $\approx150$ individuals
                from each genus
        \end{myitemize}
        \column{.5\textwidth}
        \includegraphics[width=\textwidth]{../images/photos/cyrt-agusanensis.jpg} \quad
        \includegraphics[width=\textwidth]{../images/photos/gekko-mindorensis.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{More data---preliminary results}
    Results for 1000 loci from 5 pairs of \emph{Gekko mindorensis} populations\\

    \begin{center}
        \includegraphics<1->[height=5.5cm]{../images/number-of-divs-gekko-mindorensis.pdf}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{More power}
    \begin{itemize}[<+->]
        \item Full-likelihood Bayesian implementation \footnote{\tiny\shortfullcite{JeetDiss}}
            \begin{itemize}
                \item Uses all the information in the sequence data
                \item Applicable to much deeper timescales
                \item \ldots Currently inefficient
            \end{itemize}
        \item Working to incorporate new developments on analytical integration
            of gene trees \footnote{\tiny\shortfullcite{Bryant2012}}
            \begin{itemize}
                \item Very efficient numerical approximation of posterior 
                \item Applicable to NGS datasets
            \end{itemize}
    \end{itemize}
\end{frame}

@@

    \begin{center}
        \includegraphics<1>[height=6.5cm]{../images/dmc-cartoon-no-islands-pop-shared-middle-wide.pdf}
        \includegraphics<2>[height=6.5cm]{../images/dmc-cartoon-no-islands-pop-phylogeny.pdf}
    \end{center}
\end{frame}

@@

\begin{frame}
    \frametitle{Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
    \end{columns}
\end{frame}

\begin{frame}[t]
    \frametitle{West-Central Africa}
    \begin{center}
        \includegraphics<1->[height={3cm}]{../../../../Dropbox/field-photos/africa/Figure2_WAmapForestDist.png}
        \hspace{0.3mm}
        \includegraphics<1->[height={3cm}]{../../../../Dropbox/field-photos/africa/Figure4_herps.jpeg}
    \end{center}

    \uncover<2->{
    \begin{center}
        \includegraphics[height=4.5cm]{../images/number-of-divs-africa.pdf}
    \end{center}
    }
\end{frame}

\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/malaysia/malaysia-burungs.jpg}
    \end{columns}
\end{frame}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-present.png}}
\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
\end{frame}
}
